\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2019-08-16 sections/results.tex
Add: Update table 1

  We have developed \hl{mindpipe}, a flexible and modular pipeline for 16S data analysis.
  It incorporates various popular, publicly available tools as well as custom Python modules and scripts to facilitate inference of co-occurrence networks from 16S data.
  The pipeline workflow is as shown in Figure~\ref{fig:figure1}, it supports the conversion of raw 16S sequence data or counts matrices into co-occurrence networks through multiple methods.
  Each process in the pipeline supports alternate tools for performing the same task, users can use the configuration file to change these values.
  We perform a systematic analysis of each step of the pipeline to determine the set of default options for the pipeline (Table~\ref{tab:default_options}).
  We also provide the users with a set of guidelines to facilitate tool selection as appropriate for their data.

  \begin{table}[h]
    \centering
    \small
    \begin{tabular}{|c|c|c|}
      %\begin{tabularx}{\textwidth}{XXXX}
      \hline
      \textbf{Process} & \textbf{Tool} & \textbf{Parameters} \\
      \hline
      Denoising and Clustering & Dada2 & ?? \\
      Taxonomy Assignment & \ac{ncbi} + Blast & ?? \\
      OTU Processing & Dynamic cutoff & ?? \\
      Network Inference & Consensus & ?? \\
      \hline
    \end{tabular}
    %\end{tabularx}
    \caption{Default tools and parameters for the pipeline}
    \label{tab:default_options}
  \end{table}

>>>>

  We have developed \hl{mindpipe}, a flexible and modular pipeline for 16S data analysis, that allows us to infer co-occurence networks from 16S sequencing data.
  It incorporates various popular, publicly available tools as well as custom Python modules and scripts to facilitate inference of co-occurrence networks from 16S data.
  It allows for using any combination of the incorporated tools for intermediate analyses construct the networks.
  The pipeline workflow is as shown in Figure~\ref{fig:figure1}, it supports the conversion of raw 16S sequence data or counts matrices into co-occurrence networks through multiple methods.
  Each process in the pipeline supports alternate tools for performing the same task, users can use the configuration file to change these values.
  We perform a systematic analysis of each step of the pipeline to determine the set of default options for the pipeline (Table~\ref{tab:default_options}).
  We also provide the users with a set of guidelines to facilitate tool selection as appropriate for their data.

  % TODO: Update this table
  \begin{table}[h]
    \centering
    \small
    \begin{tabular}{|c|c|c|}
      \hline
      \textbf{Process} & \textbf{Tool} & \textbf{Parameters} \\
      \hline
      Denoising and Clustering & Dada2/Deblur & default \\
      Taxonomy Assignment & \ac{ncbi} with Blast & RefSeq database \\
      OTU Processing & Based on statistical power & Dynamic cutoff \\
      Network Inference & Consensus method & - \\
      \hline
    \end{tabular}
    \caption{Default tools and parameters for the pipeline}
    \label{tab:default_options}
  \end{table}
